### 2017-07-16 ThesisText/background.tex
Made corrections

K-Means is a clustering algorithm that find $ K $ clusters in data. The $ K $
variable is given to the algorithm as an argument, hence the name K-Means. The
algorithm works by creating $ K $ random points based on the features of the
data. The algorithm then iterates updating the location of those points until
they converge.~\cite{book_ml,book_dm_practical}

@@

Affinity Propagation is another clustering algorithm, but this one does not
take a number of clusters as an argument. This algorithm finds the optimal
number of clusters.~\cite{book_ml,book_dm_practical}

>>>>

K-Means is a clustering algorithm that finds $ K $ clusters in data. The $ K $
variable is given to the algorithm as an argument, hence the name K-Means. The
algorithm works by creating $ K $ random points based on the features of the
data.

Each point has has many coordinates as there are features, and the domains of
the coordinates correspond to the domains of the features. Each object in the
data gets associated with the closets point to it. A set of objects associated
with the same point is called a cluster.

The algorithm then iterates updating the location of those points by
calculating the center of of the cluster until convergence is
reached.~\cite{book_ml,book_dm_practical}

@@

Affinity Propagation is another clustering algorithm, but this one does not
take a number of clusters as an argument. This algorithm finds the optimal
number of clusters.

To find clusters, the algorithm keeps two matrices, a responsibility matrix and
an availability matrix. Each matrix relates each point in the data to every
other point. Each step of the algorithm iterates by updating the information on
these matrices until there is convergence.

~\cite{book_ml,book_dm_practical}

### 2017-07-16 ThesisText/data.tex
Made corrections

The provided sheets contain information of courses, students, their activities
in Moodle, and their results. The data comes from Moodle databases and from the
SIIUE system. Both systems are integrated, making Moodle plus SIIUE the
University's own~\gls{lms}.

@@

\begin{itemize}
    \item \texttt{UCs\_SIIUE\_Moodle.csv}
    \item \texttt{complete\_rate.csv}
    \item \texttt{completed.csv}
    \item \texttt{Notas UCS SIIUE.csv}
    \item \texttt{Profile}
    \item \texttt{ResultadosUCMoodle}
    \item \texttt{Correlação}
    \item \texttt{Alunos SIIUE E-L}
    \item \texttt{AlunosMoodle}
    \item \texttt{export\_weekly}
    \item \texttt{export\_activity}
\end{itemize}

@@

The rest of the sheets contains the objects which are going to be used in the
Data Mining tasks. Those objects and their features are fairly unorganized in
the original data, so an analysis on of the available features had to be done.
Section~\ref{sec:objs_feat} states the objects found in the data and details
their features. Section~\ref{sec:preproc_dataset} shows how the final dataset
is organized.

@@

After a first analysis of the data, the objects are identified. These objects
are courses, students, results, etc. Data mining tasks are applied over these
objects which are described by their features.

@@

Professors have only the features listed in table~\ref{tab:professor_features}.
The data contains a field called \textit{Role} which states if that Moodle user
is a professor or a student. If the user is a professor the role has a value of
5. If it is a student, it has a value of 3. A few users with a value of 4 are
present. These users have the role of editor, but the Moodle logs only have 11
entries for a user of this role, so they are simply discarded.

@@

    \begin{tabular}{l l}
        Feature                 & Data Type \\ \hline
        \textit{MoodleUsername} & String    \\
        \textit{Name}           & String    \\
    \end{tabular}

>>>>

The provided sheets contain information of courses, students, their activities
in Moodle, and their results. The data comes from Moodle databases and from the
SIIUE system. SIIUE is the integrated information system of the university. It
is the system which contains information on courses, students, their grades,
among many other things. Both systems are integrated, making Moodle plus SIIUE
the University's own~\gls{lms}.

@@

\begin{itemize}
    \item \texttt{UCs\_SIIUE\_Moodle.csv}
    \item \texttt{complete\_rate.csv}
    \item \texttt{completed.csv}
    \item \texttt{Notas UCS SIIUE.csv}
    \item \texttt{Profile}
    \item \texttt{ResultadosUCMoodle}
    \item \texttt{Correlação}
    \item \texttt{Alunos SIIUE E-L}
    \item \texttt{AlunosMoodle}
    \item \texttt{export\_weekly}
    \item \texttt{export\_activity}
    \item \texttt{CalculosAlunos.csv}
\end{itemize}

@@

The rest of the sheets contains the objects which are going to be used in the
Data Mining tasks. Those objects and their features are fairly unorganized in
the original data, so an analysis of the available features had to be done.
Section~\ref{sec:objs_feat} states the objects found in the data and details
their features. Section~\ref{sec:preproc_dataset} shows how the final dataset
is organized.

@@

After a first analysis of the data, the objects are identified. These objects
are courses, Moodle users, results, profile, and Moodle logs. Data mining tasks
are applied over these objects which are described by their features.

@@

Professors have only the features listed in table~\ref{tab:professor_features}.
The data contains a field called \textit{Role} which states if that Moodle user
is a professor or a student. If the user is a professor the role has a value of
5. If it is a student, it has a value of 3. A few users with a value of 4 are
present. These users have the role of editor, but the Moodle logs only have 10
entries for a user of this role, so they are simply discarded.

@@

    \begin{tabular}{l l}
        Feature                 & Data Type \\ \hline
        \textit{MoodleUsername} & String    \\
        \textit{Name}           & String    \\
        \textit{Role}           & Enumerated \\
    \end{tabular}

### 2017-07-16 ThesisText/experiments.tex
Made corrections

    \caption
        [Students, Courses, Logs, and Results]
        {Students, Courses, Logs, and Results. This dataset joins information
        from four processed datasets in order to relate a student, a course,
        usage data from that student on that course, and the final grade of it}

@@

    \caption
        [Predicting student's grades based on Moodle usage results]
        {Predicting student's grades based on Moodle usage results. Two models
        are trained 10 times on three different variations of the same dataset.
        The maximum, minimum, and average accuracy is displayed for those ten
        executions.}

@@

    \caption
        [Clustering Student's Grades Based on Moodle Usage]
        {Clustering Student's Grades Based on Moodle Usage. The table displays
        the results for the silhouette score for clustering. The values for
        every variant of the dataset are approximately the same, so only one
        table is shown.}

>>>>

    \caption
        [Students, Courses, Logs, and Results]
        {Students, Courses, Logs, and Results.}

@@

    \caption
        [Predicting student's grades based on Moodle usage results]
        {Predicting student's grades based on Moodle usage results.}

@@

    \caption
        [Clustering Student's Grades Based on Moodle Usage]
        {Clustering Student's Grades Based on Moodle Usage.}

### 2017-07-16 ThesisText/statistics.tex
Made corrections

    \caption
        [Number of Students per Course and Number of Approved Students per
        Course]
        {Number of Students per Course and Number of Approved Students per
        Course. The grey bars show the number of students, while the blue bars
        show the number of approved students. The graph}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_0_HIS10755_all}
        \caption[]{}
        \label{subfig:stat_least_004_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_1_MAT7515_all}
        \caption[]{}
        \label{subfig:stat_least_004_1_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_0_HIS10755_cud}
        \caption[]{}
        \label{subfig:stat_least_004_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_1_MAT7515_cud}
        \caption[]{}
        \label{subfig:stat_least_004_1_cud}
    \end{subfigure}

@@

    \caption
        [Total number of active courses per week (Bars) vs total active courses (Left)]
        {Total number of active courses per week (Bars) vs total active courses (Left).}

@@

Table~\ref{tab:results_stats} shows some statistics on the results data. We see
that from the available 716 entries, 334 of the, refer to instances of a
student getting approved on a course.

>>>>

    \caption
        [Number of Students per Course and Number of Approved Students per
        Course]
        {Number of Students per Course and Number of Approved Students per
        Course.}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_0_PED9078_all}
        \caption[]{}
        \label{subfig:stat_least_004_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_1_HIS10755_all}
        \caption[]{}
        \label{subfig:stat_least_004_1_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_0_PED9078_cud}
        \caption[]{}
        \label{subfig:stat_least_004_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_least_1_HIS10755_cud}
        \caption[]{}
        \label{subfig:stat_least_004_1_cud}
    \end{subfigure}

@@

    \caption
        [Total number of active courses per week vs total active courses]
        {Total number of active courses per week (Bars) vs total active courses (Line).}

@@

Table~\ref{tab:results_stats} shows some statistics on the results data. We see
that from the available 716 entries, 334 refer to instances of a student
getting approved on a course.
